taxize - taxonomic search and retrieval in R

### 2013-05-28 inst/doc/taxize_withcode.Rnw
fixed references

\begin{table}[!ht]
\caption{Data sources used in taxize, tasks available, and links to them}
\label{tab:a} % title of Table
\begin{tabular}{|l|cccc|l|}
\hline
Source name & Name search & Name resolution & Phylogeny & Sequences & URL  \\
\hline
Encyclopedia of Life & Yes & See GNR below & No & No & \url{http://eol.org/} \\
Integrated Taxonomic Information System & Yes & Synonyms & No & No & \url{http://www.itis.gov/} \\
iPlant Taxonomic Name Resolution Service & Yes & Yes & No & No & \url{http://bit.ly/16dHkBy} \\
Phylomatic & No & No & Yes & No & \url{ http://bit.ly/P0pjMz} \\
uBio & Yes & Yes & No & No & \url{http://www.ubio.org/} \\
Global Names Resolver & Yes & Yes & No & No & \url{http://bit.ly/11R3Pbr} \\
Global Names Index & Yes & No & No & No & \url{http://bit.ly/11R3RQB} \\
IUCN Red List & Yes & No & No & No & \url{http://bit.ly/11R3RQC} \\
Tropicos & Yes & Yes & No & No & \url{http://www.tropicos.org/} \\
Plantminer & Yes & No & No & No & \url{http://www.plantminer.com/} \\
The Plant List & Yes & Yes & No & No & \url{http://www.theplantlist.org/} \\
Catalogue of Life & Yes & Yes & No & No & \url{http://bit.ly/11R3S75} \\
National Center for Biotechnology Information & Yes & X & Yes \footnote{Web only, no API, see \url{http://1.usa.gov/11R446a}} & Yes & \url{http://www.ncbi.nlm.nih.gov/} \\
\hline
\end{tabular}
\end{table}

New data sources can be added; we may add the following sources: Wikispecies and The Tree of Life. Get in touch with one of the authors if you would like any data sources added.

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{REF}, ecological networks \cite{REF}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example.

<<phylomaticphylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE>>=
# Input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

# Plot the tree
plot(tree, cex=1)
@

>>>>

\begin{table}[!ht]
\caption{Data sources used in taxize, tasks available, and links to them}
\label{tab:a} % title of Table
\begin{tabular}{|l|cccc|l|}
\hline
Source name & Name search & Name resolution & Phylogeny & Sequences & URL  \\
\hline
Encyclopedia of Life \citep{eol} & Yes & See GNR below & No & No & \url{http://eol.org/} \\
Integrated Taxonomic Information System \citep{itis} & Yes & Synonyms & No & No & \url{http://www.itis.gov/} \\
iPlant Taxonomic Name Resolution Service \citep{tnrs} & Yes & Yes & No & No & \url{http://bit.ly/16dHkBy} \\
Phylomatic \citep{webb2005} & No & No & Yes & No & \url{ http://bit.ly/P0pjMz} \\
uBio \citep{ubio} & Yes & Yes & No & No & \url{http://www.ubio.org/} \\
Global Names Resolver \citep{eolgnr} & Yes & Yes & No & No & \url{http://bit.ly/11R3Pbr} \\
Global Names Index \citep{eolgnr} & Yes & No & No & No & \url{http://bit.ly/11R3RQB} \\
IUCN Red List \citep{iucn} & Yes & No & No & No & \url{http://bit.ly/11R3RQC} \\
Tropicos \citep{tropicos} & Yes & Yes & No & No & \url{http://www.tropicos.org/} \\
Plantminer \citep{carvalho2010plantminer} & Yes & No & No & No & \url{http://www.plantminer.com/} \\
The Plant List & Yes & Yes & No & No & \url{http://www.theplantlist.org/} \\
Catalogue of Life \citep{col} & Yes & Yes & No & No & \url{http://bit.ly/11R3S75} \\
National Center for Biotechnology Information \citep{ncbi} & Yes & X & Yes \footnote{Web only, no API, see \url{http://1.usa.gov/11R446a}} & Yes & \url{http://www.ncbi.nlm.nih.gov/} \\
\hline
\end{tabular}
\end{table}

New data sources can be added; we may add the following sources: Wikispecies and The Tree of Life. A connection to \url{freshwaterecology.info} \citep{freshwaterecology} (a database with autecological characteristics, ecological preferences and biological traits as well as distribution patterns of more than 12.000 European freshwater organisms belonging to fish, macro-invertebrates, macrophytes, diatoms and phytoplankton) will be finished when their new API will be released. Get in touch with one of the authors if you would like any data sources added.

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{webb2002phylogenies}, ecological networks \cite{REF}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example:

\begin{figure}[!h] 
\centering 
<<phylomaticphylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE>>=
# Input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

# Plot the tree
plot(tree, cex=1)
@
\caption{A Phylogeny for the three species.} 
\end{figure}

### 2013-05-28 inst/doc/taxize_withcode.tex
fixed references

One data source available in taxize is available in another R pacakge that solely interact with that data source. We provide a few convenience functions that wrap functions in \emph{taxonstand}, an R interface to The Plant List \cite{theplantlist}.

\begin{table}[!ht]
\caption{Data sources used in taxize, tasks available, and links to them}
\label{tab:a} % title of Table
\begin{tabular}{|l|cccc|l|}
\hline
Source name & Name search & Name resolution & Phylogeny & Sequences & URL  \\
\hline
Encyclopedia of Life & Yes & See GNR below & No & No & \url{http://eol.org/} \\
Integrated Taxonomic Information System & Yes & Synonyms & No & No & \url{http://www.itis.gov/} \\
iPlant Taxonomic Name Resolution Service & Yes & Yes & No & No & \url{http://bit.ly/16dHkBy} \\
Phylomatic & No & No & Yes & No & \url{ http://bit.ly/P0pjMz} \\
uBio & Yes & Yes & No & No & \url{http://www.ubio.org/} \\
Global Names Resolver & Yes & Yes & No & No & \url{http://bit.ly/11R3Pbr} \\
Global Names Index & Yes & No & No & No & \url{http://bit.ly/11R3RQB} \\
IUCN Red List & Yes & No & No & No & \url{http://bit.ly/11R3RQC} \\
Tropicos & Yes & Yes & No & No & \url{http://www.tropicos.org/} \\
Plantminer & Yes & No & No & No & \url{http://www.plantminer.com/} \\
The Plant List & Yes & Yes & No & No & \url{http://www.theplantlist.org/} \\
Catalogue of Life & Yes & Yes & No & No & \url{http://bit.ly/11R3S75} \\
National Center for Biotechnology Information & Yes & X & Yes \footnote{Web only, no API, see \url{http://1.usa.gov/11R446a}} & Yes & \url{http://www.ncbi.nlm.nih.gov/} \\
\hline
\end{tabular}
\end{table}

New data sources can be added; we may add the following sources: Wikispecies and The Tree of Life. Get in touch with one of the authors if you would like any data sources added.

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{REF}, ecological networks \cite{REF}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Input the taxonomic names}
taxa <- \hlfunctioncall{c}(\hlstring{"Poa annua"}, \hlstring{"Abies procera"}, \hlstring{"Helianthus annuus"})

@@

>>>>

One data source available in taxize is available in another R package that solely interact with that data source. We provide a few convenience functions that wrap functions in \emph{taxonstand}, an R interface to The Plant List \cite{theplantlist}.

\begin{table}[!ht]
\caption{Data sources used in taxize, tasks available, and links to them}
\label{tab:a} % title of Table
\begin{tabular}{|l|cccc|l|}
\hline
Source name & Name search & Name resolution & Phylogeny & Sequences & URL  \\
\hline
Encyclopedia of Life \citep{eol} & Yes & See GNR below & No & No & \url{http://eol.org/} \\
Integrated Taxonomic Information System \citep{itis} & Yes & Synonyms & No & No & \url{http://www.itis.gov/} \\
iPlant Taxonomic Name Resolution Service \citep{tnrs} & Yes & Yes & No & No & \url{http://bit.ly/16dHkBy} \\
Phylomatic \citep{webb2005} & No & No & Yes & No & \url{ http://bit.ly/P0pjMz} \\
uBio \citep{ubio} & Yes & Yes & No & No & \url{http://www.ubio.org/} \\
Global Names Resolver \citep{eolgnr} & Yes & Yes & No & No & \url{http://bit.ly/11R3Pbr} \\
Global Names Index \citep{eolgnr} & Yes & No & No & No & \url{http://bit.ly/11R3RQB} \\
IUCN Red List \citep{iucn} & Yes & No & No & No & \url{http://bit.ly/11R3RQC} \\
Tropicos \citep{tropicos} & Yes & Yes & No & No & \url{http://www.tropicos.org/} \\
Plantminer \citep{carvalho2010plantminer} & Yes & No & No & No & \url{http://www.plantminer.com/} \\
The Plant List & Yes & Yes & No & No & \url{http://www.theplantlist.org/} \\
Catalogue of Life \citep{col} & Yes & Yes & No & No & \url{http://bit.ly/11R3S75} \\
National Center for Biotechnology Information \citep{ncbi} & Yes & X & Yes \footnote{Web only, no API, see \url{http://1.usa.gov/11R446a}} & Yes & \url{http://www.ncbi.nlm.nih.gov/} \\
\hline
\end{tabular}
\end{table}

New data sources can be added; we may add the following sources: Wikispecies and The Tree of Life. A connection to \url{freshwaterecology.info} \citep{freshwaterecology} (a database with autecological characteristics, ecological preferences and biological traits as well as distribution patterns of more than 12.000 European freshwater organisms belonging to fish, macro-invertebrates, macrophytes, diatoms and phytoplankton) will be finished when their new API will be released. Get in touch with one of the authors if you would like any data sources added.

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{webb2002phylogenies}, ecological networks \cite{REF}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example:

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Input the taxonomic names}
taxa <- \hlfunctioncall{c}(\hlstring{"Poa annua"}, \hlstring{"Abies procera"}, \hlstring{"Helianthus annuus"})

@@

\caption{A Phylogeny for the three species.} 
\end{figure}
